Optimal Peak Shaving with Bifacial Solar PV: Simulated Storage Battery Dispatch for Electric Vehicle Charging Load

### 2023-12-22 Paper/paper.tex
paper v3 with 25 sources

@@

Technical peak shaving refers to the case where a load must operate under a technical limitation such as a maximum power agreement or distribution transformer size. The load power must remain under the threshold at all times, otherwise, overcurrent protection may be activated or permanent damage to equipment such as lines or transformers. Even if the current is technically able to rise above the threshold, doing so may violate a contract regarding maximum load power. The important consideration is that the economic cost of exceeding the threshold is prohibitively high. The time resolution of technical peak shaving control may need to be as low as seconds or milliseconds \cite{Iannarelli2020}. Although technical peak shaving is complicated by a large network, many assets, or a dynamic threshold, from the perspective of dispatching the assets to shave the peak the problem is relatively simple. Technical peak shaving might be performed on current or apparent power rather than active power.

@@

@@

\begin{equation}
  \label{eq:net-load}
  \begin{split}
    & \text{Given:} \\
    NL & = L - S                                                               \\
    SL & = NL - B_d + B_c                                 \\
    & \exists B_d, B_c \text{ s.t. } T \ge SL \forall t \\
       & \text{where:}                                                         \\
       NL(t) & \in \mathbb{R} [kW] \text{ is the net load time series }         \\
       L(t) & \in \mathbb{R}^+ [kW] \text{ is the EV charging load time series } \\
       S(t) &\in \mathbb{R}^+ [kW] \text{ is the solar production time series }                \\
       SL(t) & \in \mathbb{R} [kW] \text{ is the site load time series seen at the electric meter }         \\
       B_c(t) & \in \mathbb{R}^+ [kW] \text{ is the battery charging load time series }  \\
       B_d(t) &\in \mathbb{R}^+ [kW] \text{ is the battery discharge time series }   \\
       T(t) &\in \mathbb{R}^+ [kW] \text{ is power threshold }   \\
  \end{split}
\end{equation}

@@

\begin{equation}
  \label{eq:cost}
  \begin{split}
    C_m & = \sum_k^K [p_{p,k,m}  max(SL^+_{k,m})] + \sum_k^K [p_{e,k,m} \sum (SL^+_{k,m}) ] \\
        & \text{where:}                                                                                           \\
        SL_{k,m}^+(t) &= SL(t) \forall SL(t)>0 \text{ in TOU period $k$ and month $m$} \\
        C_m & \in \mathbb{R}^+ [\$] \text{ is total retail electric cost for month}\ m\                                             \\
        p_{p,k,m} & \in \mathbb{R}^+ [\$/kW] \text{ is power price for TOU period}\ k\ \text{and month}\ m\                         \\
        p_{e,k,m} & \in \mathbb{R}^+ [\$/kWh] \text{ is energy price for TOU period}\ k\ \text{and month}\ m\                       \\
        K & \in \mathbb{Z}^+ \text{ is the number of TOU periods}
  \end{split}
\end{equation}

@@

\begin{table}[!h]
  \centering
  \caption{Total Retail Electric Cost. Simulated total retail electric cost for three of the case studies (some omitted for conciseness) over the 10 months of available data and a given battery capacity. Cost reduction is calculated with respect to the South 20° base case. The best reduction in total retail cost is \$1422 for the 50\% West 90° case.}
  \label{tab:total-cost}
  \begin{tabularx}{\textwidth}{XXXXXXXX}
    \toprule
    Battery $[kWh]$ & Cost South 20° $[\$]$ & Cost 50\% West 90° $[\$]$ & Cost 100\% West 90° $[\$]$ & Cost Reduction 50\% West 90° $[\$]$ & Cost Reduction 100\% West 90° $[\$]$ & Cost Reduction 50\% West 90° $[\%]$ & Cost Reduction 100\% West 90° $[\%]$ \\
    \midrule
    25              & 31314                 & 30391                     & 31730                      & 923                                 & -416                                 & 3.0                                 & -1.3                                 \\
    50              & 27132                 & 25773                     & 27022                      & 1359                                & 110                                  & 5.0                                 & 0.4                                  \\
    75              & 23893                 & 22775                     & 23625                      & 1118                                & 268                                  & 4.7                                 & 1.1                                  \\
    100             & 21229                 & 19807                     & 20804                      & \textbf{1422}                       & 425                                  & 6.7                                 & 2.0                                  \\
    125             & 18954                 & 17623                     & 18564                      & 1331                                & 390                                  & 7.0                                 & 2.1                                  \\
    150             & 17094                 & 15886                     & 17286                      & 1208                                & -192                                 & 7.1                                 & -1.1                                 \\
    200             & 14547                 & 13689                     & 15282                      & 858                                 & -735                                 & 5.9                                 & -5.0                                 \\
    400             & 10730                 & 10969                     & 12131                      & -239                                & -1401                                & -2.2                                & -13.1                                \\
    600             & 8859                  & 9140                      & 10333                      & -281                                & -1474                                & -3.2                                & -16.6                                \\
    \bottomrule
  \end{tabularx}
\end{table}

>>>>

Even in cases where the electric load isn't growing, large solar photovoltaic (PV) arrays relative to the load will create relative peaks and dips in the net load seen by the network as clouds pass overhead. As the solar ramp-down rate due to clouds can be much faster than the ramp-up rate of many traditional thermal generators, grid operators will need to predict and anticipate these relative peaks. With an all-sky camera and machine vision algorithms, 15-minute nowcasting cloud identification may only reach 84.2\% accuracy \cite{Nespoli2022}. The remaining peaks will likely need to be managed by battery or other energy storage systems with extremely fast power ramp rates.

@@

Technical peak shaving refers to the case where a load must operate under a technical limitation such as a maximum power agreement or distribution transformer size. The load power must remain under the threshold at all times, otherwise, overcurrent protection may be activated or permanent damage to equipment such as lines or transformers \cite{Greco2023}. Even if the current is technically able to rise above the threshold, doing so may violate a contract regarding maximum load power. The important consideration is that the economic cost of exceeding the threshold is prohibitively high. The time resolution of technical peak shaving control may need to be as low as seconds or milliseconds. Although technical peak shaving is complicated by a large network, many assets, or a dynamic threshold, from the perspective of dispatching the assets to shave the peak the problem is relatively simple. Technical peak shaving might be performed on current or apparent power rather than active power.

@@

In the literature, peak shaving strategies that dispatch a battery system often don't consider the retail cost of energy and rarely use an optimized threshold approach or vertical bifacial solar PV. In \cite{Reihani2016} authors forecast load and choose a state of charge (SOC) trajectory to manage load peaks. Solar power smoothing is applied in works such as \cite{Lavrova2012}. Linear programming optimization in \cite{Lee2014} reduces the on-peak load of residential EV charging by dispatching a battery. In \cite{Gazafroudi2018} a multi-agent system buys and sells energy in a local energy market for a residence with solar PV and a dispatchable vehicle-to-home EV battery. In \cite{Zheng2015} authors optimize peak shaving based on a rate tariff and a technical power threshold. Distributed solar PV  helps reduce net load and tracking arrays produce more energy in the late afternoon \cite{Faranda2011} but the increase may be reduced by common backtracking methods \cite{Dolara2012}. Vertical bifacial has been benchmarked in the literature and evaluated for new applications such as public highway solar installations \cite{Niccolai2022}. Vertical bifacial solar is coupled with a storage battery in \cite{Wallberg2022} and in \cite{Castellucci2022} with a rule-based peak shaving algorithm, reducing EV charging load peaks by 38.6\% and 79\%, respectively. However, the retail energy cost isn't estimated and a comparison is not made to understand the relative merit of vertical bifacial compared to south-facing modules.

@@

  \begin{equation}
    \label{eq:net-load}
    \begin{split}
             & \text{Given:}                                                                        \\
      NL     & = L - S                                                                              \\
      SL     & = NL - B_d + B_c                                                                     \\
             & \exists B_d, B_c \text{ s.t. } T \ge SL \forall t                                    \\
             & \text{where:}                                                                        \\
      NL(t)  & \in \mathbb{R} [kW] \text{ is the net load time series }                             \\
      L(t)   & \in \mathbb{R}^+ [kW] \text{ is the EV charging load time series }                   \\
      S(t)   & \in \mathbb{R}^+ [kW] \text{ is the solar production time series }                   \\
      SL(t)  & \in \mathbb{R} [kW] \text{ is the site load time series seen at the electric meter } \\
      B_c(t) & \in \mathbb{R}^+ [kW] \text{ is the battery charging load time series }              \\
      B_d(t) & \in \mathbb{R}^+ [kW] \text{ is the battery discharge time series }                  \\
      T(t)   & \in \mathbb{R}^+ [kW] \text{ is power threshold }                                    \\
    \end{split}
  \end{equation}

@@

  \begin{equation}
    \label{eq:cost}
    \begin{split}
      C_m           & = \sum_k^K [p_{p,k,m}  max(SL^+_{k,m})] + \sum_k^K [p_{e,k,m} \sum (SL^+_{k,m}) ]         \\
                    & \text{where:}                                                                             \\
      SL_{k,m}^+(t) & = SL(t) \forall SL(t)>0 \text{ in TOU period $k$ and month $m$}                           \\
      C_m           & \in \mathbb{R}^+ [\$] \text{ is total retail electric cost for month}\ m\                 \\
      p_{p,k,m}     & \in \mathbb{R}^+ [\$/kW] \text{ is power price for TOU period}\ k\ \text{and month}\ m\   \\
      p_{e,k,m}     & \in \mathbb{R}^+ [\$/kWh] \text{ is energy price for TOU period}\ k\ \text{and month}\ m\ \\
      K             & \in \mathbb{Z}^+ \text{ is the number of TOU periods}
    \end{split}
  \end{equation}

@@

\begin{table}[!h]
  \centering
  \caption{Total Retail Electric Cost. Simulated total retail electric cost for three of the case studies (some omitted for conciseness) over the 10 months of available data and a given battery capacity. Cost reduction is calculated with respect to the South 20° base case. The best reduction in total retail cost is \$1422 for the 50\% West 90° case.}
  \label{tab:total-cost}
  \begin{tabularx}{\textwidth}{XXXXXXXX}
    \toprule
    Battery $[kWh]$ & \multicolumn{3}{l}{Cost $[\$]$} & \multicolumn{2}{l}{Cost Reduction $[\$]$} & \multicolumn{2}{l}{Cost Reduction $[\%]$}                                                                   \\
                    & South 20°                       & 50\% West 90°                             & 100\% West 90°                            & 50\% West 90° & 100\% West 90° & 50\% West 90° & 100\% West 90° \\
    \midrule
    25              & 31314                           & 30391                                     & 31730                                     & 923           & -416           & 3.0           & -1.3           \\
    50              & 27132                           & 25773                                     & 27022                                     & 1359          & 110            & 5.0           & 0.4            \\
    75              & 23893                           & 22775                                     & 23625                                     & 1118          & 268            & 4.7           & 1.1            \\
    100             & 21229                           & 19807                                     & 20804                                     & \textbf{1422} & 425            & 6.7           & 2.0            \\
    125             & 18954                           & 17623                                     & 18564                                     & 1331          & 390            & 7.0           & 2.1            \\
    150             & 17094                           & 15886                                     & 17286                                     & 1208          & -192           & 7.1           & -1.1           \\
    200             & 14547                           & 13689                                     & 15282                                     & 858           & -735           & 5.9           & -5.0           \\
    400             & 10730                           & 10969                                     & 12131                                     & -239          & -1401          & -2.2          & -13.1          \\
    600             & 8859                            & 9140                                      & 10333                                     & -281          & -1474          & -3.2          & -16.6          \\
    \bottomrule
  \end{tabularx}
\end{table}
